Rapid cycleway prioritisation tool

### 2020-05-29 code/index.Rmd
Add toc

---
title: "Rapid cycleway prioritisation tool"
author: "University of Leeds"
output: html_document
---

@@

## PRELIMINARY RESULTS

@@

## Introduction

@@

### Map layers

The maps show five layers.

1) Key network:

- we have created this to represent the most important cycle corridors. For this layer, we do not take into account the width of the roads, but simply represent them as continuous corridors. This underscores the importance of ensuring that cycle routes are continuous and do not 'give up' at awkward junctions. To derive this layer, we have selected all road segments with cycle potential in the 85th percentile and above, which also belong to classified trunk roads, A roads or B roads. These segments are then joined together to form a continuous network.

2) Existing cycleways (500m +)

- this layer shows existing cycleways. This may be helpful to view in connection with the other layers, because it can reveal where gaps in the existing cycle network could be filled by new infrastructure. This layer does not include some on-road cycle lanes or cycleways less than 500m in length, but these can be viewed in one of the basemap options (see below for more information about the basemaps).

@@

3) Spare lane(s)

- these are routes that have more than one vehicle lane in either direction and have a cycling potential above the minimum threshold (which varies according to region as it needs to be higher in e.g. Greater London than in rural areas).

4) Width >= 10m

- these routes are at least 10m in width and have a cycling potential above the minimum threshold.

5) Top routes

- these are the top routes for pop-up cycleways according to our analysis. These roads have either a spare lane or width of at least 10m, and are ranked according to their mean cycling potential. For routes that are shorter than 1km in length, we use 'km_cycled' instead of mean cycling potential - this is simply the cycling potential multiplied by the length of the route. We used certain eligibility criteria for the top routes, for example, a road which already has an existing cycleway alongside the majority of its length cannot be a top route. Top routes are listed in the table below the map, so you can see more information on them. The number of top routes selected is normally 20, with some variation by region.

@@

### Basemaps

>>>>

---
title: "Rapid cycleway prioritisation tool"
author: "Dr Robin Lovelace & Dr Joey Talbot, Institute for Transport Studies, University of Leeds"
output: 
  html_document: 
    toc: yes
---

@@

# NOTE: PRELIMINARY RESULTS

@@

# Introduction

@@

# Map layers

The maps contain five layers of data that overlay the basemaps.

## 1. Key network:

This layer is designed to represent a cohesive network of direct routes.
It shows what a joined-up cycle network could look like if there were no constraints on road space, along some of the most important corridors.
The layer takes no account spare space and is designed to support consideratioin of alternative options, e.g. one way streets, where there may be insufficient space for road space reallocation without changing the navigable network for motor traffic.
The layer was developed based on evidence on the importance of active transport network that are continuous and do not 'give up' at awkward junctions.
The layer was created by selecting all road segments with cycle potential in the 85th percentile and above, which also belong to classified trunk roads, A roads or B roads.
These segments are then joined together to form a continuous network.

## 2. Existing cycleways

This layer shows existing cycleways. This may be helpful to view in connection with the other layers, because it can reveal where gaps in the existing cycle network could be filled by new infrastructure. This layer does not include some on-road cycle lanes or cycleways less than 500m in length, but these can be viewed in one of the basemap options (see below for more information about the basemaps).

@@

## 3. Spare lane(s)

These are routes that have more than one vehicle lane in either direction and have a cycling potential above the minimum threshold (which varies according to region as it needs to be higher in e.g. Greater London than in rural areas).

## Width >= 10m

These routes are at least 10m in width and have a cycling potential above the minimum threshold.

## Top routes

These are the top routes for pop-up cycleways according to our analysis. These roads have either a spare lane or width of at least 10m, and are ranked according to their mean cycling potential. For routes that are shorter than 1km in length, we use 'km_cycled' instead of mean cycling potential - this is simply the cycling potential multiplied by the length of the route. We used certain eligibility criteria for the top routes, for example, a road which already has an existing cycleway alongside the majority of its length cannot be a top route. Top routes are listed in the table below the map, so you can see more information on them. The number of top routes selected is normally 20, with some variation by region.

@@

# Basemaps
